{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis}

### 2025-07-08 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes, a lot

% ==============================================================================
\section{Nesterov's Accelerated Gradient}
    \subsection{In preparations}
        \begin{assumption}[smooth add nonsmooth]\label{ass:smooth-plus-nonsmooth}
            The function $F = f + g$ where $f:\RR^n \rightarrow \RR$ is an $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
            The function $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function. 
        \end{assumption}
        \begin{assumption}[admitting minimizers]\label{ass:smooth-plus-nonsmooth-x}
            Let $F = f + g$ and in addition assume that the set of minimizers $X^+ := \argmin_{x}F(x)$ is non-empty. 
        \end{assumption}

        \begin{definition}[Proximal gradient operator]
            Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
            Let $\beta > 0$. 
            Then, we define the proximal gradient operator $T_{\beta}$ as 
            \begin{align*}
                T_\beta (x | F) &= \argmin{z} \left\lbrace
                    g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{\beta}{2}\Vert z - x\Vert^2
                \right\rbrace. 
            \end{align*}
        \end{definition}
        \begin{remark}
            If the function $g \equiv 0$, then it yields the gradient descent operator $T_\beta(x) = x - \beta^{-1}\nabla f(x)$. 
            In the context where it's clear what the function $F = f + g$ is, we simply write $T_\beta(x)$ for short. 
        \end{remark}

@@

        \begin{definition}[R-WAPG sequence]\label{def:rwapg-seq}
            Let $(L_k)_{k \ge 0}$ be a sequence such that $L_k > \mu$ for all $k$. 
            Let $\alpha_0 \in (0, 1]$, $(\alpha_k)_{k \ge 1}$ has $\alpha_k \in (\mu/ L_k, 1)$. 
            Then define for all $k \ge 0$: 
            \begin{align*}
                \rho_k(1 - \alpha_{k + 1})\alpha_k^2 = \alpha_{k + 1}(\alpha_{k + 1} - \mu/L_k). 
            \end{align*}
        \end{definition}
        \begin{remark}
            When $\rho_k = 1$, the recursive relation between $\alpha_k, \alpha_{k - 1}$ is the same as the well known Nesterov's sequence used in algorithm such as FISTA and Nesterov's accelerated gradient. 
            See Li and Wang \cite{li_relaxed_2025} for more information. 
        \end{remark}
        % \begin{definition}[similar triangle representation of NAPG]\;\label{def:st-method}\\
        %     Let $(\alpha_k)_{k \ge 0}$ be an R-WAPG sequence. 
        %     Suppose that the base case $v_{-1}, x_{k - 1}\in \RR^n$ is given to initialize the algorithm. 
        %     Then the algorithm produces the sequence of iterates $(y_k, x_k, v_k)_{k \ge 0}$ and auxiliary parameter sequence $L_k, \tau_k$ satisfying these inequalities: 
        %     \begin{align*}
        %         & \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}, 
        %         \\
        %         & y_k = (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1},
        %         \\
        %         & D_f(x_k, y_k) \le L_k/2\Vert x_k - y_k\Vert^2, 
        %         \\
        %         & x_k = T_{L_k}(y_k),
        %         \\
        %         & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
        %     \end{align*} 
        % \end{definition}
        % The following theorems are critical in analyzing the behavior of algorithm in Definition \ref{def:st-method}.

@@

@@

@@

        \begin{definition}[SNAPG-V2]\label{def:snapg-v2}
            Let $F$ satisfies Assumption \ref{ass:sum-of-many}. 
            Let $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$. 
            Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
            The SNAPG generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
                & (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right), \\
                & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
                & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
                & x_k =  T_{L_k}(y_k | F_{I_k}) \text{ s.t: } D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
        \begin{lemma}[range of the momentum sequence in SNAPG-V2]\;\label{lemma:snapg-v2-seq-range}\\

@@

@@

                (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right). 

@@

                \item Solution to the equation with $\alpha_k > 0$ is given by: 

@@

                        - \alpha_{k - 1}^2 + \frac{\mu}{L_{k - 1}}

@@

                                \alpha_{k - 1} - \frac{\mu}{L_{k - 1}}

@@

                    \right). 

@@

@@

            \begin{proof}[proof of \ref{lemma:snapg2-itrs-props-item1}]

@@

            \begin{proof}[proof of \ref{lemma:snapg2-itrs-props-item2}]

@@

@@

                &\le \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 

@@

                \item[(c)] The sequence $(\alpha_k)_{k \ge 0}$ has $(L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right)$. It is a special case of Definition \ref{def:rwapg-seq} with $\rho_{k - 1} = L_{k - 1}/L_k$. 

@@

                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2}. 

@@

                        + \frac{\alpha_k(\mu - \mu^{(i)})}{2}

@@

                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2

@@

                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2

@@

                        + \frac{\alpha_k(\mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2

@@

                        \frac{\alpha_k(\mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2

@@

                        \frac{\alpha_k(\mu - \mu^{(I_k)})}{2} 

@@

@@

            \begin{proof}[Proof of (f)]

@@

            \begin{proof}[Proof of (g)]

@@

                    \frac{L_k\alpha_k(\alpha_k - \mu/L_k)}{2} 

@@

                    - \frac{L_k\alpha_k(\alpha_k - \mu/L_k)}{2} 

@@

                        \mu - \mu^{(i)}

@@

                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2}

@@

                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2}. 

@@

    \subsection{\textcolor{purple}{So, what to do next?}}
        Hi Arron would you like to add me for the co-authorship to continue this line of work and see how Nesterov's Accelerated Technique may work out for the stochastic gradient method? 
        These results are solid results but, they are still partial results and, below are the potential I foresee for this these ideas. 
            \item Narrow down the sequence $\alpha_k$ and make sure that it can allow the quantity: 
                \mathbb E_k\left[
            is negative, or at least bounded. I am not sure how this will work out, but I have some solid ideas around it. 
            \item Roll up the inequality in Theorem \ref{thm:snapg2-one-step} recursively and, determine the convergence rate through $\alpha_k$ that makes the previous item true. 
            In addition, I have the hunches that the convergence rate involves the variance of $\mu^{(I_k)}$ and, it will slower than the non-stochastic case of the algorithm. 
        For the future we can: 
            \item Extend the definition of strong convexity to relative strong convexity with respect to a quasi-norm. This would extend interpolation hypothesis in Assumption \ref{ass:interp-hypothesis} where, even if $\mu > 0$, it doesn't mean that $F$ has a unique solution through strong convexity. This is entirely possible and appeared in the literatures before so, I can give you the words of confidence. 
            \item Show the convergence of the method for objective function based on quasi-strong convexity. This is a much weaker assumption it works well in practice for the common known problems in convex programming. 

>>>>

% ==============================================================================
\section{Nesterov's Accelerated Gradient}
    \subsection{In preparations}
        Assumption \ref{ass:smooth-plus-nonsmooth} states the standard assumption of smooth plus non-smooth structured optimization problems for proximal gradient based algorithm. 
        Assumption \ref{ass:smooth-plus-nonsmooth-x} adds the assumption for the existence of minimizers. 
        Definition \ref{def:pg-opt} is the definition of the proximal gradient operator, which is equivalent to the gradient descent operator when the non-smooth part of the objective is the zero function. 
        \par
        Finally, to show the convergence of a stochastic case of the Nesterov's accelerated proximal gradient, we prepared Lemma \ref{thm:jesen} and, \ref{thm:pg-ineq}. 
        They are crucial in the derivation of the convergence. 
        The derivation for the convergence rate of a stochastic accelerated variant of Nester's accelerated  proximal gradient method is in the next section. 
        \begin{assumption}[smooth add nonsmooth]\label{ass:smooth-plus-nonsmooth}
            The function $F = f + g$ where $f:\RR^n \rightarrow \RR$ is an $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex function. 
            The function $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function. 
        \end{assumption}
        \begin{assumption}[admitting minimizers]\label{ass:smooth-plus-nonsmooth-x}
            Let $F = f + g$ and in addition assume that the set of minimizers $X^+ := \argmin_{x}F(x)$ is non-empty. 
        \end{assumption}

        \begin{definition}[Proximal gradient operator]\label{def:pg-opt}
            Suppose $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
            Let $\beta > 0$. 
            Then, we define the proximal gradient operator $T_{\beta}$ as 
            \begin{align*}
                T_\beta (x | F) &= \argmin{z} \left\lbrace
                    g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{\beta}{2}\Vert z - x\Vert^2
                \right\rbrace. 
            \end{align*}
        \end{definition}
        \begin{remark}
            If the function $g \equiv 0$, then it yields the gradient descent operator $T_\beta(x) = x - \beta^{-1}\nabla f(x)$. 
            In the context where it's clear what the function $F = f + g$ is, we simply write $T_\beta(x)$ for short. 
        \end{remark}

@@

        % \begin{definition}[R-WAPG sequence]\label{def:rwapg-seq}
        %     Let $(L_k)_{k \ge 0}$ be a sequence such that $L_k > \mu$ for all $k$. 
        %     Let $\alpha_0 \in (0, 1]$, $(\alpha_k)_{k \ge 1}$ has $\alpha_k \in (\mu/ L_k, 1)$. 
        %     Then define for all $k \ge 0$: 
        %     \begin{align*}
        %         \rho_k(1 - \alpha_{k + 1})\alpha_k^2 = \alpha_{k + 1}(\alpha_{k + 1} - \mu/L_k). 
        %     \end{align*}
        % \end{definition}
        % \begin{remark}
        %     When $\rho_k = 1$, the recursive relation between $\alpha_k, \alpha_{k - 1}$ is the same as the well known Nesterov's sequence used in algorithm such as FISTA and Nesterov's accelerated gradient. 
        %     See Li and Wang \cite{li_relaxed_2025} for more information. 
        % \end{remark}
        % \begin{definition}[similar triangle representation of NAPG]\;\label{def:st-method}\\
        %     Let $(\alpha_k)_{k \ge 0}$ be an R-WAPG sequence. 
        %     Suppose that the base case $v_{-1}, x_{k - 1}\in \RR^n$ is given to initialize the algorithm. 
        %     Then the algorithm produces the sequence of iterates $(y_k, x_k, v_k)_{k \ge 0}$ and auxiliary parameter sequence $L_k, \tau_k$ satisfying these inequalities: 
        %     \begin{align*}
        %         & \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}, 
        %         \\
        %         & y_k = (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1},
        %         \\
        %         & D_f(x_k, y_k) \le L_k/2\Vert x_k - y_k\Vert^2, 
        %         \\
        %         & x_k = T_{L_k}(y_k),
        %         \\
        %         & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
        %     \end{align*} 
        % \end{definition}
        % The following theorems are critical in analyzing the behavior of algorithm in Definition \ref{def:st-method}.

@@

        \begin{definition}[semi quasi strong convexity (\textcolor{red}{NEW})]\label{def:sq-scnvx}
            A function $f:\RR^n \rightarrow \overline \RR$ is semi quasi strongly convex if, there exists a constant $\mu \ge 0$ and, a non-zero linear mapping $A: \RR^n\rightarrow \RR^m$ such that for all $x \in \RR^n, y \in RR^n$ and $\lambda \in [0, 1]$ it satisfies:
                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\mu\lambda(1 - \lambda)}{2} \Vert A(y - x)\Vert^2. 
        \begin{remark}
            It is strong convexity but instead of being strongly convex to the function $\mu/2\Vert \cdot\Vert^2$, it's $x \mapsto \mu/2\Vert Ax \Vert^2$ instead. 
            This is an example of uniform convexity because it also fits in Bauchke \cite[Definition 10.7]{bauschke_convex_2017}, with $\phi = \Vert A\Vert^2\Vert x - y\Vert^2$. 
        \end{remark}

@@

            Consequently, each of the $F_i$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth-x} with $X_i$ being the set of minimizers and, under interpolation hypothesis this equates to non-empty intersections between all $X_i$, i.e: $\bigcap_{i = 1}^n X_i \neq \emptyset$. 

@@

        What is the weakest possible sequence one can use for the accelerated proximal gradient based algorithm that utilizes a strong convexity constant? 
        If we were to use the developed convergence framework for Nesterov's accelerated proximal gradient, negative momentum and, negative convergence (lower bound instead of upper bound) should be prohibited, and it means that the sequence $(\alpha_k)_{k \ge 0}$ which is going to appear in the proposed algorithm (See Definition \ref{def:snapg-v2}) must satisfy the condition $\alpha_k \in (0, 1]$ for all $k \ge 0$. 
        The following lemma with a blunt name should clarify the sufficient conditions required for the sequence to make sense. 
        \begin{lemma}[weakest possible momentum sequence that makes sense \textcolor{red}{NEW}]\;\label{lemma:snapg-v2-seq-range}\\

@@

            Suppose that $(\tilde\mu_k)_{k\ge 0}$ is another non-negative sequence. 

@@

                (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 
                &= \alpha_{k}\left(\alpha_{k} - \tilde \mu_k/L_k\right). 

@@

                \item The expression of $\alpha_k$ based on previous $\alpha_{k - 1}$ is given by: 

@@

                        - \alpha_{k - 1}^2 + \frac{\tilde\mu_k}{L_{k - 1}}

@@

                                \alpha_{k - 1} - \frac{\tilde\mu_k}{L_{k - 1}}

@@

                    \right) &\ge 0. 

@@

            For all $k \ge 1$, re-arranging the equality it comes to solving the following equality: 
                0 &= L_k\alpha_k^2 - \tilde\mu_k\alpha_k + L_{k - 1}\alpha_{k - 1}^2\alpha_k - L_{k - 1}\alpha_{k - 1}^2
                &= L_k\alpha_k^2 + (L_{k - 1}\alpha_{k - 1}^2 - \tilde \mu_k)\alpha_k - L_{k - 1}\alpha_{k - 1}^2
                \iff 0 &=
                \alpha_k^2 + L_k^{-1}(L_{k - 1}\alpha_{k - 1}^2 - \tilde \mu_k)\alpha_k - L_k^{-1}L_{k - 1}\alpha_{k - 1}^2
                \iff 
                \alpha_k &= 
                \frac{1}{2}\left(
                    -L^{-1}_k(L_{k - 1} \alpha_{k - 1}^2 - \tilde\mu_k)
                        L_k^{-2}(L_{k - 1}\alpha_{k - 1}^2 - \tilde \mu_k)^2
                        + 4L_k^{-1}L_{k - 1} \alpha_{k - 1}^2
                &= \frac{L_{k-1}}{2L_k}\left(
                    - \alpha_{k - 1}^2 + \frac{\tilde \mu_k}{L_{k - 1}}
                            \alpha_{k - 1}^2 - \frac{\tilde \mu_k}{L_{k - 1}}
                        \right)^2 + \frac{4L_k}{L_{k - 1}}\alpha_{k - 1}^2
            Here, we take the positive root of the quadratic so that it ensures $\alpha_k \ge 0$. 
            This is true by induction. 
            If $\alpha_{k - 1} \ge 0$ then the $\frac{4L_k}{L_{k - 1}}\alpha_{k - 1}^2 \ge 0$ hence, the square root is greater than the term outside it so, $\alpha_k \ge 0$ too. 
            Assume inductively that $\alpha_{k - 1} \ge 0$. 
            Next, we want to find the conditions needed such that $\alpha_k < 1$. 
            To start, we complete the square root inside the square root: 
                0&\le 
                    \alpha_{k - 1}^2 - \frac{\tilde \mu_k}{L_{k - 1}}
                \right)^2 + \frac{4L_k}{L_{k - 1}}\alpha_{k - 1}^2
                &= \alpha_{k - 1}^4 + \left(\frac{\tilde \mu_k}{L_{k - 1}}\right)^2
                - 2\alpha_{k - 1}^2 \frac{\tilde \mu_k}{L_{k - 1}} 
                + \frac{4L_k}{L_{k - 1}}\alpha_{k - 1}^2
                &= \alpha_{k - 1}^4 + \left(\frac{\tilde \mu_k}{L_{k - 1}}\right)^2
                + \alpha_{k - 1}^2 \left(
                    \frac{-2\tilde \mu_k}{L_{k - 1}} + \frac{4L_k}{L_{k - 1}}. 
                &= \alpha_{k - 1}^4 + \left(\frac{\tilde \mu_k}{L_{k - 1}}\right)^2
                + \alpha_{k - 1}^2 \left(
                    \frac{4L_k - 2\tilde \mu_k}{L_{k - 1}}
                &= \alpha_{k - 1}^4
                + \alpha_{k - 1}^2 \left(
                    \frac{4L_k - 2\tilde \mu_k}{L_{k - 1}}
                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
                + \left(\frac{\tilde \mu_k}{L_{k - 1}}\right)^2
                &= \left(
                    \alpha_{k - 1}^2 + 
                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
                + \left(\frac{\tilde \mu_k}{L_{k - 1}}\right)^2
                    \alpha_{k - 1}^2 + 
                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
                    \tilde \mu_k^2 - 4L_k^2 - \tilde \mu_k^2 + 4L_k\tilde \mu_k
                }{L_{k - 1}^2}
                    \alpha_{k - 1}^2 + 
                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
                    4L_k \tilde \mu_k - 4L_k^2
                }{L_{k - 1}^2}
                    \alpha_{k - 1}^2 + 
                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
                4\left(
                    \frac{L_k}{L_{k - 1}}\cdot \frac{\tilde \mu_k}{L_{k - 1}} - 1
                &< 
                    \alpha_{k - 1}^2 + 
                    \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
                \right)^2. 
            On the last inequality, we used our assumption that the sequence $\tilde\mu_k, L_k$ satisfies $\frac{\tilde \mu_k}{L_{k - 1}} < \frac{L_{k - 1}}{L_k}$. 
            Substitute it back into the expression previous obtained for $\alpha_k$, using the monotone property of the function $\sqrt{\cdot}$, it gives the inequality 
                \alpha_k & < 
                \frac{L_{k-1}}{2L_k}\left(
                    - \alpha_{k - 1}^2 + \frac{\tilde \mu_k}{L_{k - 1}}
                            \alpha_{k - 1}^2 + 
                            \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
                \frac{L_{k-1}}{2L_k}\left(
                    - \alpha_{k - 1}^2 + \frac{\tilde \mu_k}{L_{k - 1}}
                    + \alpha_{k - 1}^2 + \frac{2L_k - \tilde \mu_k}{L_{k - 1}}
                \right) = 1. 
        \begin{remark}
            Let's do some sanity check for the lemma we just derived. 
            The sequence $L_k$ will be from the Lipschitz line search routine of the accelerated proximal gradient method. 
                \item Let's assume the obvious choice of $L_k = \max_{i = 1, \ldots,n} K^{(i)}$ for all $k = 1, 2, \ldots$ given an objective function $F$ satisfying Assumption \ref{ass:sum-of-many}. 
                Then, the sufficient condition for the second item translates to $\tilde\mu_i/L_k < 1$. 
                Hence, if we choose $\tilde \mu_i$ to be a constant sequence of $0$ then it works out to have $\alpha_k \in (0, 1)$ for all $k = 1, 2, \ldots$. 
                If $F$ has $L \ge \mu$ so, the function is non-trivial, then choose $\tilde \mu_i = \mu$, the true strong convexity parameter then it also works out. 
                \item Let's assume that some type of monotone line search routine is used for the algorithm making $L_0 \le L_1 \le \ldots \le L_k \le \ldots$ to be a non-decreasing sequence, then it requires $\tilde \mu_k / L_{k - 1} \le L_{k - 1}/L_k$. 
                Well, it will still make sense because one such choice could be $\tilde \mu_k = \rho\min_{i = 1, \ldots, k} L_{i - 1}/L_i$ for some $\rho \in (0, 1)$. 

        \end{remark}
        % --------------------------------------------------------------------------------------------------------------
        \begin{definition}[SNAPG-V2]\label{def:snapg-v2}
            Let $F$ satisfies Assumption \ref{ass:sum-of-many}. 
            Let $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$. 
            Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
            \textcolor{red}{Let $\tilde \mu \ge 0$ be a fixed constant.}
            The SNAPG generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
            \begin{align*}
                & \alpha_k \in (0, 1): (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \tilde \mu/L_k\right), \\
                & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
                & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
                & L_k > 0: D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
                & x_k =  T_{L_k}(y_k | F_{I_k}), \\
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
            \end{align*}
        \end{definition}
        \begin{remark}
            $\tilde \mu_k, L_k$ are not necessary a random variable because they are determined by a line-search like conditions, consequently $(\alpha_k)_{k\ge 0}$, whether they are a random variable depends on the line search procedures. 
            Otherwise, all the iterates $(x_k, y_k, z_k)$ are random variable determined by $I_k$ when conditioned on all previous $I_{k - 1}, I_{k - 2}, \ldots, I_{0}$. 
            \par
            \textcolor{red}{NEW}. One may notice that $\alpha_k$ requires $L_k$ which comes before $L_k, x_k$ which are needed in advanced for $\alpha_k$. 
            This may seems off since no algorithm can know what $L_k$ to choose in advanced to determine the line search. 
            But, it is important to note that in here, we defined a sequence of conditions on the iterates $x_k, y_k, z_k$, and auxilary sequences $\alpha_k, L_k$ which is not a definition of any algorithm. 
            It is quantifying the conditions needed for an algorithm that actually implements it.
            \par
            For the trivial case where we don't need to worry about it is when $L_k = \max_{i = 1, \ldots, n} K^{(i)}$. 
            See Chambolle, Calatroni \cite{calatroni_backtracking_2019} for an implementations of linear search with backtracking for the FISTA algorithm, it is how one would implement it in the deterministic case. 
        \end{remark}

@@

            \textbf{Proof of \ref{lemma:snapg2-itrs-props-item1}}. 

@@

            \textbf{proof of \ref{lemma:snapg2-itrs-props-item2}.}

@@

                    + \frac{\alpha_k(\tilde\mu - \mu)}{2} 
                    \Vert \bar x - v_{k - 1}\Vert^2. 

@@

                \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 

@@

                \item[(c)] The sequence $(\alpha_k)_{k \ge 0}$ has $(L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right)$. 

@@

                    + \frac{\alpha_k(\tilde \mu_k - \mu^{(i)})}{2}. 

@@

                        + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}
                    \Vert \bar x - v_{k - 1}\Vert^2

@@

                    + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2

@@

                    + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2

@@

                        + \frac{\alpha_k(\tilde \mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2

@@

                        \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2

@@

                        \frac{\alpha_k(\tilde\mu - \mu^{(I_k)})}{2} 

@@

                    \frac{\alpha_k(\tilde\mu - \mu)}{2} 
                    \Vert \bar x - v_{k - 1}\Vert^2

@@

            \textbf{Proof of (f)}. 

@@

            \textbf{Proof of (g)}.

@@

                \frac{L_k\alpha_k(\alpha_k - \tilde \mu/L_k)}{2} 

@@

                - \frac{L_k\alpha_k(\alpha_k - \tilde \mu/L_k)}{2} 

@@

                    \tilde \mu - \mu^{(i)}

@@

                + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}

@@

                + \frac{\alpha_k(\tilde \mu - \mu^{(i)})}{2}. 

@@

    \subsection{convergence rate of the algorithm under various circumstances}

    \subsection{\textcolor{purple}{So, what to do next?}}
        Hi Arron would you like to add me for the co-authorship to continue this line of work and see how Nesterov's Accelerated Technique may work out for the stochastic gradient method? 
        These results are solid results but, they are still partial results and, below are the potential I foresee for this these ideas. 
        \begin{enumerate}
            \item Narrow down the sequence $\alpha_k$ and make sure that it can allow the quantity: 
            \begin{align*}
                \mathbb E_k\left[
                        \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
            \end{align*}
            is negative, or at least bounded. I am not sure how this will work out, but I have some solid ideas around it. 
            \item Roll up the inequality in Theorem \ref{thm:snapg2-one-step} recursively and, determine the convergence rate through $\alpha_k$ that makes the previous item true. 
            In addition, I have the hunches that the convergence rate involves the variance of $\mu^{(I_k)}$ and, it will slower than the non-stochastic case of the algorithm. 
        \end{enumerate}
        For the future we can: 
        \begin{enumerate}
            \item Extend the definition of strong convexity to relative strong convexity with respect to a quasi-norm. This would extend interpolation hypothesis in Assumption \ref{ass:interp-hypothesis} where, even if $\mu > 0$, it doesn't mean that $F$ has a unique solution through strong convexity. This is entirely possible and appeared in the literatures before so, I can give you the words of confidence. 
            \item Show the convergence of the method for objective function based on quasi-strong convexity. This is a much weaker assumption it works well in practice for the common known problems in convex programming. 
        \end{enumerate}
